---
title: Homework 6
author: Hunter Rose; hrose33
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(ggplot2)
library(dplyr)
library(tidyr)
library(readr)
library(stringr)
library(tidyverse)
library(lubridate)
library(magrittr)
```

```{r}
bst_in_shw <- read_excel('KIB - Best in Show (public)1.xlsx', sheet='Best in show full sheet')
```

```{r}
dog <- bst_in_shw %>%
  select(1, 2, 3, 5, 8, 27)
colnames(dog)
head(dog$Intelligence)
#factor(dog$size)
dog$size[dog$size == 'small'] <- 5
dog$size[dog$size == 'medium'] <- 10
dog$size[dog$size == 'large'] <- 15
dog$Intelligence[as.numeric(dog$Intelligence) < 50] <- 'clever'
dog$Intelligence[as.numeric(dog$Intelligence) > 49] <- 'dumb'

```

```{r}
dog %>%
  ggplot(aes(x=dog$'datadog score', y=Popularity, color = category)) + geom_point(aes(shape=dog$'Intelligence')) + geom_text(label=dog$'Dog breed', size = 2)
```
When trying to incorporate size, I continued to get the following error: Error in grid.Call.graphics(C_setviewport, vp, TRUE) : non-finite location and/or size for viewport. I am not asking for points because I know that I should have asked but was swamped with other assignments and knew it wouldn't be anwesered in time. I got my graph to the point it was prior to incorporating size, let me know how you would incorporate size so I will know for future reference. Thanks!